---
title: "Homework 2"
output: github_document
---

This is my work for homework 2. 

```{r}
library(tidyverse)
library(readxl)
```

## Problem 1

Read and clean the Mr. Trash Wheel sheet:

```{r}
trashwheel_df = 
  read_excel(
    "./Trash-Wheel-Collection-Totals-8-6-19.xlsx",
             sheet = "Mr. Trash Wheel", 
             range = cell_cols("A:N")) %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(
    sports_balls = round(sports_balls), 
    sports_balls = as.integer(sports_balls)
    ) 
```

Read and clean precipitation data for 2017 and 2018:

```{r}
precipitation_2018 = 
  read_excel(
    "./Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2018 Precipitation", 
    skip = 1
    ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2018) %>% 
  relocate(year)
             
precipitation_2017 = 
  read_excel(
    "./Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2017 Precipitation", 
    skip = 1
    ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2017) %>% 
  relocate(year)
```

Now combine annual precipitation:

```{r}
month_df = 
    tibble(
      month = 1:12,
      month_name = month.name
    )

precipitation_df = 
  bind_rows(precipitation_2018, precipitation_2017) %>% 
  relocate(year)  
  
precip_final_df = left_join(precipitation_df, month_df, by = "month")
```

This dataset contains information about the Mr. Trash Wheel trash collector in Baltimore, Maryland. Key variables in this dataset includes year, month, weight of trash collected, and specific kinds of trash. There are a total of `r ncol(trashwheel_df)` columns in this dataset and `r nrow(trashwheel_df)` rows. 

The precipitation dataset contains information on inches of precipitation measured each month. In our consolidated dataset of precipitation in 2017 and 2018, key variables include year, month (by numeric order and name), and inches of precipitation. There are a total of `r ncol(precip_final_df)` columns and `r nrow(precip_final_df)` rows.

```{r}
precip_sum_2018 = 
  precipitation_2018 %>% 
  select(total) %>% 
  summarize_if(is.numeric, sum)
```

The total precipitation in 2018 was 70.3 inches. 

```{r}
trashwheel_2017 = 
  filter(trashwheel_df, year == 2017) %>% 
  select(sports_balls) %>% 
  summarize_if(is.numeric, median)
```

The median number of sports balls in a dumpster in 2017 was 8.

## Problem 2

Read and clean the NYC transit data. Convert the entry variable from character to a logical variable. 

```{r}
NYC_transit_df = 
    read_csv("./NYC_Transit_Subway_Entrance_And_Exit_Data (1).csv") %>% 
  janitor::clean_names() %>% 
  select(line, station_name, station_latitude, station_longitude, starts_with("route"), entry, vending, entrance_type, ada) %>% 
  mutate_at(vars(route1:route11), as.character) %>% 
  pivot_longer(route1:route11, 
      names_to = "route_number",
      names_prefix = "route",
      values_to = "route_name") %>%
  mutate(entry = recode(entry, YES = TRUE, NO = FALSE))

```

This dataset containes information on each subway entrance and exit station in New York City. Key variables include subway line, station name, latitude and longitude of the subway station, entrance type (e.g., stairs, door), if ADA compliant, if entrance is allowed, if vending, and the number and name of routes served. There are `r nrow(NYC_transit_df)` rows and `r ncol(NYC_transit_df)` columns in this dataset. 

To clean this dataset I cleaned up the dataset names and converted "entry" into a logical (true/false) variable. Originally, there were 11 route number variables contianing route names as values - to tidy this data I used combined route name and route number into two separate corresponding variables.

There are `r nrow(distinct(NYC_transit_df, line, station_name))` distinct stations in this dataset, and `r nrow(filter(NYC_transit_df, ada == TRUE))` stations are ADA compliant. There are `r nrow(filter(NYC_transit_df, vending == "NO"))` station entrances/exits without vending, and `r nrow(filter(NYC_transit_df, vending == "NO", entry == TRUE))` of them allow entrance. So `r (nrow(filter(NYC_transit_df, vending == "NO", entry == TRUE))) / (nrow(filter(NYC_transit_df, vending == "NO")))` of station entrances/exits without vending allow for entrance.


Reformat data so that route number and route name are distinct variables: 

```{r}
NYC_distinct_df =
    distinct(NYC_transit_df, station_name, line, route_number, route_name, ada) %>% 
  filter(route_name == "A")
```

`r nrow(NYC_distinct_df)` distinct stations serve the A train. Of these stations, `r nrow(filter(NYC_distinct_df, ada == TRUE))` are ADA compliant.

## Problem 3

Read and clean pols-month.csv dataset (refer to comments for further details on cleaning steps)

```{r}
politicians_df = 
  read_csv("./fivethirtyeight_datasets/pols-month.csv.") %>% 
  janitor::clean_names() %>%
  separate(mon, c("year", "month", "day")) %>%
  mutate(month = recode(month, 
                        "01" = "january", 
                        "02" = "february",
                        "03" = "march",
                        "04" = "april",
                        "05" = "may",
                        "06" = "june",
                        "07" = "july",
                        "08" = "august",
                        "09" = "september",
                        "10" = "october",
                        "11" = "november",
                        "12" = "december"
                        )) %>% 
  #Separated out "mon" variable; and
  #Replaced "month" ouput with month names
  mutate(prez_gop = ifelse(prez_gop == 0, "no", "rep")) %>%
  mutate(prez_dem = ifelse(prez_dem == 0, "no", "dem")) %>%
  unite(president, c(prez_gop, prez_dem)) %>% 
  mutate(president = recode(president, "no_dem" = "dem", "rep_no" = "rep")) %>% 
  #Used prez_gop and prez_dem to create new president variable
  subset(select = -c(day))
  #Removed day variable

```

Read and clean the snp.csv dataset. 

```{r}
snp_df = 
  read_csv("./fivethirtyeight_datasets/snp.csv.") %>%
  janitor::clean_names() %>% 
  separate(date, c("month", "day", "year"), "/") %>%
  mutate(month = recode(month, 
                        "1" = "january", 
                        "2" = "february",
                        "3" = "march",
                        "4" = "april",
                        "5" = "may",
                        "6" = "june",
                        "7" = "july",
                        "8" = "august",
                        "9" = "september",
                        "10" = "october",
                        "11" = "november",
                        "12" = "december"
                        )) %>% 
  #Separated out "date" variable to multiple columns; and
  #Replaced month output with month names
  subset(select = -c(day)) %>% 
  #Removed day variable
  relocate(year, month)
```

Read and clean the unemployment dataset:

```{r}
unemploy_df = 
  read_csv("./fivethirtyeight_datasets/unemployment.csv.") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    jan:dec, 
    names_to = "month", 
    values_to = "unemployment"
  ) %>% 
  #Tidied month and unemployment variables; and
  #Modified month variable to make output same across datasets
  mutate(month = recode(month, 
                        "jan" = "january", 
                        "feb" = "february",
                        "mar" = "march",
                        "apr" = "april",
                        "jun" = "june",
                        "jul" = "july",
                        "aug" = "august",
                        "sep" = "september",
                        "oct" = "october",
                        "nov" = "november",
                        "dec" = "december"
                        ))
```

Join the datasets by merging snp into pols, and merging unemployment into the result.

```{r}

```

