---
title: "Homework 2"
output: github_document
---

This is my work for homework 2. 

```{r}
library(tidyverse)
library(readxl)
```

## Problem 1

Read and clean the Mr. Trash Wheel sheet:

```{r}
trashwheel_df = 
  read_excel(
    "./Trash-Wheel-Collection-Totals-8-6-19.xlsx",
             sheet = "Mr. Trash Wheel", 
             range = cell_cols("A:N")) %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(
    sports_balls = round(sports_balls), 
    sports_balls = as.integer(sports_balls)
    ) 
```

Read and clean precipitation data for 2017 and 2018:

```{r}
precipitation_2018 = 
  read_excel(
    "./Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2018 Precipitation", 
    skip = 1
    ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2018) %>% 
  relocate (year)
             
precipitation_2017 = 
  read_excel(
    "./Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2017 Precipitation", 
    skip = 1
    ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2017) %>% 
  relocate (year)
```

Now combine annual precipitation:

```{r}
month_df = 
    tibble(
      month = 1:12,
      month_name = month.name
    )

precipitation_df = 
  bind_rows(precipitation_2018, precipitation_2017) %>% 
  relocate(year)  
  
precipitation_df = left_join(precipitation_df, month_df, by = "month")
```

This dataset contains information about the Mr. Trash Wheel trash collector in Baltimore, Maryland. Key variables in this dataset includes year, month, weight of trash collected, and specific kinds of trash. There are a total of `r ncol(trashwheel_df)` columns in this dataset and `r nrow(trashwheel_df)` rows. 


The total precipitation in 2018 was 
The median number of sports balls in a dumpster in 2017 was 

## Problem 2
